\chapter{Analysis and Discussion}\label{chapter:analysis_discussion}
This chapter evaluates the blockchain-based weather insurance prototype proposed in \cref{section:prototype_development} by examining the functional and non-functional aspects of the system in a thorough analysis and provides a comparative analysis of the prototype against traditional weather insurance models.

\section{Analysis of the Prototype}
In this section, we take a closer look at the prototype itself and analyze whether and how it achieves the objective of "Propose a blockchain-based weather insurance design that utilizes decentralized oracles and globally available weather data." from Chapter 1 (see \cref{section:objectives}) and the concrete requirements specified in \cref{section:requirements}. Furthermore, we discuss the limitations of the prototype and the challenges encountered during the data collection process.

\subsection{Functional Analysis}
The prototype provides a decentralized application (dApp) as the user interface, enabling the end user to interact directly with the system. Through the dApp, the user can send requests for weather insurance policies as well as insurance payouts directly to the smart contract. This interaction is possible through a digital wallet (e.g. MetaMask), which allows the user to sign in and broadcast the transaction to the Ethereum blockchain. The user experience is kept to the bare minimum in order to provide an easy-to-use system, especially for non-technical users.

In \cref{subsection:purchasePolicyFlow} and \cref{subsection:policyPayoutTrigger}, we outline how the smart contract is able to receive the relevant weather data from GCP through Chainlink. Through two separate endpoints on the side of GCP, the platform that hosts Global Surface Summary of the Day (GSOD) and Global Forecast System (GFS), Chainlink is able to access both historical and forecast weather data, making it available to the smart contract. This integration ensures decentralized access to GCP, which enables the system to meet the functional requirement of securely retrieving external weather data.

As the heart of the system, the smart contract interacts directly and indirectly with the other components, synthesizing their functions to provide a smooth and automated insurance process. In \cref{fig:purchasePolicyFlow} and \cref{fig:payoutFlow}, we illustrate the different kinds of tasks the smart contract performs. These tasks, combined with its interaction capabilities described in \cref{interaction_with_smartcontract} and its storing capability through the blockchain, enable the smart contract to fulfill its requirements specified in \cref{section:requirements}.

\subsection{Non-Functional Analysis}\label{non_functional_analysis}
To ensure that the interactions and transactions of the system are secure, we look at the most vulnerable points. Transactions within the blockchain ecosystem itself are inherently secure due to the decentralized mechanisms of the blockchain, which ensure immutable records \autocite{Cheng2020A}. Vulnerable points exist between the end user and the smart contract, since the user needs to pass sensitive data onto the blockchain and between Chainlink and GCP, since this connection bridges the gap from external weather data to the blockchain ecosystem (see \cref{subsection:ChainlinkOracle}). As described in \cref{subsection:decentralizedApp}, users interact with the smart contract through a digital wallet, such as MetaMask. These transactions are cryptographically secured with a digital signature before being broadcast onto the blockchain. This ensures that only authorized users can interact with the system and that sensitive data, such as policy details, is protected during broadcasting. On the other side of the system, we have Chainlink, which interacts in a decentralized manner with GCP, making the necessary requests from all over the globe through independent nodes (see \cref{subsection:ChainlinkOracle}). This decentralized structure mitigates the risk of a single point of failure or of tampering with the external weather data. By leveraging these robust security measures, the system effectively fulfills the security requirement specified in \cref{section:requirements}.

Unlike traditional insurance systems, which often face bottlenecks due to their reliance on centrally managed infrastructure, the proposed blockchain-based system leverages decentralized technology to simplify policy management, claims processing and payouts. However, achieving wide-range scalability remains a significant challenge. The system's reliance on the Ethereum blockchain introduces limitations due to throughput problems and high gas fees, as mentioned in Chapter 1 (see \cref{technical_challenges_chapter1}). These issues can result in delays and increased costs, particularly as the number of users and transactions grows. While decentralized networks like Chainlink and widely available datasets from GCP support global applicability, the combination of technical and economic constraints of the Ethereum blockchain limits the efficient scaling of the system to accommodate a large user base across different regions and jurisdictions. With these scalability problems, there is no efficient solution for creating a global and scalable blockchain-based system that can successfully mitigate the systemic risk of traditional models. Thus, the scalability requirement is not fulfilled.

Transparency is a key aspect of the proposed system, with all transactions, policies and claims immutably recorded on the Ethereum blockchain. In \cref{subsection:purchasePolicyFlow} and \cref{subsection:policyPayoutTrigger}, it becomes evident that all the different data involved is centrally accessible through the smart contract. In a concrete implementation of the prototype, the smart contract needs to ensure that the data is stored and presented accordingly. Such an implementation could include tools like dashboards or published records to make the activity on the smart contract more accessible to non-technical users.

The proposed system fulfills the technical requirements by leveraging Ethereum as the blockchain platform where the smart contract is running, Chainlink oracles for data retrieval in a decentralized manner and GCP for access to reliable weather datasets. The integration and combination of these components, outlined in \cref{subsection:generalOverview}, \cref{subsection:policyPayoutTrigger} and \cref{subsection:purchasePolicyFlow}, ensure the system can perform all its functional requirements.

\subsection{Limitations}\label{analysis_limitations}
While the blockchain-based weather insurance system offers significant advantages over traditional models, it also comes with trade-offs and limitations. In this subsection, we focus on three key limitations, which include scalability challenges, regulatory challenges and user adoption.

\subsubsection{Scalability Challenges}\label{scalability_challenges_analysis}
Scalability is heavily influenced by the underlying Ethereum blockchain, which has limited transaction throughput. High congestion in the network can lead to increased gas fees and slower transaction processing times. These issues pose challenges with a large user base, especially during times of high demand, such as a natural disaster, where the system could become congested, leading to significantly increased gas fees. In \cref{non_functional_analysis} we mention how the requirement for a scalable system was not achieved in the proposed solution. This marks a key limitation in the blockchain-based prototype, which also reduces its applicability in real-world scenarios, since solutions for weather-related disasters like the one described in \cref{disaster_relief} require a scalable system to mitigate centralized weather-related risks.

\subsubsection{Regulatory Challenges}
The regulatory challenges presented in Chapter 1 (see \cref{regulatory_challenges_chapter1}) significantly affect the feasibility of implementing the blockchain-based weather insurance prototype. These challenges originate from the innovative and decentralized nature of blockchain technology, which often exist outside traditional and centralized legal frameworks. 

A key part of regulatory considerations in a blockchain-based insurance system is compliance with local licensing requirements. In most parts of the world, approvals or licenses are required to operate legally as an insurance provider. Furthermore, a decentralized system may conflict with centralized oversight, as existing regulatory frameworks are designed for centralized entities, where oversight is conducted through reporting, audits and direct communication with regulatory authorities. A blockchain-based system, which by nature lacks a central authority or entity, may create conflicts with these established systems of oversight. An example is the lack of universal legal recognition for smart contracts, which creates uncertainty, especially for applications such as disaster relief and renewable energy, where automated payouts rely on enforceable agreements. If smart contracts are not legally binding, their ability to reduce bureaucracy and ensure efficient operations is greatly diminished if not eliminated.

Compliance with consumer protection and data privacy regulations also poses challenges. Automated transactions may conflict with local laws if users are unable to contest or reverse them. This is particularly problematic in consumer-facing applications like tourism insurance, where disputes over denied payouts can erode trust. Furthermore, the immutable nature of blockchain data storage may conflict with privacy laws, such as the GDPR's "right to be forgotten", limiting the system's applicability in regions with strict data regulations.

Cross-border transactions further complicate the system's scalability. The decentralized architecture relies on interoperability across jurisdictions, each with different requirements for taxation, anti-money laundering (AML) policies and know-your-customer (KYC) compliance. These regulatory differences can introduce inefficiencies and operational complexities, impacting the system's core advantages of transparency, efficiency and trust. Interoperability across borders is also essential for addressing systemic risk described in \cref{systemic_risk}. Without seamless operations, bureaucratic processes across different jurisdictions could reduce the system's perceived efficiency, which limits its ability to scale globally. Coupled with the technical scalability challenges discussed in \cref{scalability_challenges_analysis}, these regulatory barriers further diminish the feasibility of developing a global and scalable solution.

\subsubsection{User Adoption}
The adoption of new technologies, especially in rural areas, often faces challenges based on skepticism and unfamiliarity. Many individuals have prejudices against emerging technologies like blockchain, viewing them as too complex, untrustworthy or unnecessary \autocite{Alabdali2023Influential}. This skepticism can result in slower user adoption rates than what might be expected based on the system's rational benefits and capabilities outlined in this thesis.

Additionally, the proposed system introduces unique concepts, such as digital wallets, dApps and smart contracts, which require a basic level of technical understanding. This can act as an entry barrier for individuals who have limited time or access to educational resources. The time and effort needed to understand the system's functionality and advantages may discourage users from engaging with a blockchain-based system, further slowing adoption.

\subsection{Challenges in Data Collection}
The data collection process for analyzing and designing the prototype faced several challenges, originating from the evolving nature of blockchain technology and the inherent complexity of insurance systems. These challenges span technical and organizational domains, both of which must be addressed to ensure the validity of the proposed system.

One of the primary challenges is the rapid evolution of blockchain technology. While it does offer innovative aspects like decentralization, transparency and automation, the technology is still in its early stages, with frequent updates to technical documentation and shifts in standards. Ensuring compatibility between blockchain components, decentralized oracles and real-world weather data requires continuous monitoring and adaptation, adding complexity to the data collection process.

Additionally, insurance systems are highly complex, involving numerous components that influence policy design, premium calculation, risk assessment and claim management. Collecting comprehensive research to address these variables requires synthesizing diverse sources. However, these data sources often vary significantly in their format and scope, such as structured datasets, unstructured text, historical or current information. The granularity of this data can differ as well, with some sources providing localized information while others offer only high-level insights, making it challenging to align and analyze the data consistently. Moreover, the reliability of these sources can be inconsistent, with some being prone to errors, omissions or outdated information. Consideration of these variations necessitates the use of data transformation and validation techniques to ensure a cohesive and accurate representation of the overall system.

\section{Comparative Analysis}\label{comparitive_analysis}
In this chapter, we compare the blockchain-based approach used in our prototype with the traditional weather insurance model. The analysis presents key areas where our blockchain-based system offers significant improvements, while simultaneously addressing limitations and potential trade-offs.

\subsection{Efficiency and Bureaucracy}\label{efficiency_bureaucracy}
Traditional insurance models are often hindered by extensive bureaucracy and manual processes. Policy creation, eligibility checks and claim payouts often involve multiple intermediaries, leading to increased administrative costs. In \cref{subsection:purchasePolicyFlow} and \cref{subsection:policyPayoutTrigger}, we present how, in a blockchain-based system, these inefficiencies can be eliminated through automated processes. A key part of that automation is the capabilities of smart contracts and blockchain technology, enabling the retrieval and validation of external data, such as weather and user data, through decentralized oracles and decentralized apps (dApps). Such a system not only reduces bureaucratic expenses but also accelerates processing time, which greatly benefits the end user.

Furthermore, a dApp interface provides the user with a single point of access, simplifying the interaction process and eliminating the communication challenges often encountered in traditional models, such as complex paperwork or lengthy approval processes. This streamlined approach gives the blockchain-based system a significant advantage for spontaneous and short-term insurance needs, such as travel insurance (see \cref{tourism_industry}).

\subsection{User Interaction and Trust}\label{user_interaction_and_trust}
The proposed blockchain-based weather insurance system significantly improves user interaction while bolstering trust through its transparent and decentralized design. In traditional models, users interact only with the front-end interface of an insurance provider, without insights into the backend processes. Our proposed solution offers users a clear view of the system's backend processes through the record-keeping of the smart contract on the blockchain. This transparency not only enhances the user experience by providing greater confidence in the system's operations but also bolsters trust by ensuring that all transactions and processes are verifiable and immutable.

By combining the intuitive user interface of a dApp and its security features with the reliability and transparency of blockchain technology, the system not only simplifies user interaction but also builds a foundation of trust, addressing two key challenges faced by traditional insurance models.

\subsection{Accessibility and Transparency}\label{accessibility_transparency}
Traditional insurance models often rely on centralized offices and intermediaries, which can limit their reach to users in local environments. The proposed system, in contrast, can operate through a dApp anywhere in the world where sufficient internet infrastructure exists. Combined with the digital wallet, which can hold the necessary cryptocurrency, the system enables policy creation, eligibility checks and payouts without the need for cumbersome documentation or in-person visits. This accessibility is particularly beneficial for individuals and businesses in regions vulnerable to extreme weather events and lacking insurance infrastructure. Moreover, users of the proposed system can view the entire lifecycle of their insurance policy, from policy creation to payout. This level of transparency can enhance trust and user engagement, particularly among users in regions where confidence in traditional companies is inherently low. By combining an easily accessible interface with transparent blockchain record-keeping, the proposed system offers a reliable, trustworthy solution to weather-based insurance needs.